---
title: "Cell size determination as an input in cell-based declustering using standardized Ripley's K function"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Install and load required packages for this step of the workflow

```{r}
library(spatstat)
library(jsonlite)
library(rjson)
library(reticulate)
library(sp)
library(maptools)
library(rgeos)
library(KneeArrower)
```

#Set the working directory

```{r}
setwd("~/Documents/UT/Research/PyCharm/SSADC/Warm Up To be Transferred/Current Scripts/SSADC Multiple Realization Example")
```

#Load the datafile using the X, Y, and porosity dataframe exported to JSON from the Jupyter notebook for all realizations

```{r}
data <- fromJSON(file="XYcoords.json")
```


#Run the standardized ripley's K using 1000 simulations at a confidence interval of 95% and estimate the maximum curvature of the departure from complete stationary random (CSR) as the cell size input for declustering

```{r}

cellsize <- {}
opt_curv <-  {}


for(i in (1:10)){      # 1:max nos of realizations made i.e. the dataset
  x<-data[2*i-1]
  y<-data[2*i]
  
  x_min <- sapply(x, min)
  y_min <- sapply(y, min)
  x_max <- sapply(x, max)
  y_max <- sapply(y, max)
  
  biased <- ppp(as.numeric(unlist(x)), as.numeric(unlist(y)), c(x_min, x_max), c(y_min, y_max)) # try for x and y ranges c(0,1000)
  
  test_env <- envelope(biased, fun=Lest, correction="best", nsim = 100) #try 1000 bootstrap simulations
  
  df <- data.frame("radius"=test_env$r, "obs"=test_env$obs, "hi"=test_env$hi, "low" =test_env$lo, "theo"=test_env$theo, "diff"=(test_env$obs-test_env$hi))

  index <-  match(max(df$diff),df$diff)[1] # gives the first index with the max departure from CSR in case of duplicity

  opt_cell <- df$radius[index] # find optimal cell size

  cellsize <- append(cellsize, opt_cell) # append optimal cell size to list
  
  cuttoff.point <- findCutoff(df$radius, df$obs, method="curvature") # find maximum curvature 

  curv <- cuttoff.point[1] #pick radius at max. curvature

  opt_curv <- c(opt_curv,curv) # append r_curv to list
  
   
}
```

#Let's manipulate the cell size inputs obtained into a dataframe and save to a csv file that can be exported into the jupyter notebook

```{r}
test <-  do.call(rbind,list(cellsize))
test <- t(test)
test2 <- do.call(rbind,opt_curv)
df_k <-  data.frame(test,test2) # create dataframe
colnames(df_k)<- c("max_dep","max_curv")
rownames(df_k)=NULL #reset row indexes
write.csv(df_k,'cellsizes_Ripley_Multiple_Realizations.csv')

```

